---
title: "Reig_Jaume_Exercise1_Omics"
author: "Jaume"
date: "22 de mayo de 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Introduction
Pulmonary CDC11c+ cells from young and middle-age animal.

# Summary
Analysis of pulmonary CDC11c+ cells from 6-8 week and 10-13 month old C57BL/6 animals. CDC11c+ cells are key modulators of the immune response in the lung. Results provide insight into molecular mechanisms underlying the decline in immune function associated with aging.

# Organism
Mus musculus

#Data descriptions
Eight samples of mice; 4 from middle-age and 4 from young mice. Two groups

# Citation
Vijay R, Hua X, Meyerholz DK, Miki Y et al. Critical role of phospholipase A2 group IID in age-related susceptibility to severe acute respiratory syndrome-CoV infection. J Exp Med 2015 Oct 19;212(11):1851-68. PMID: 26392224

# Exercise 1 starts here
```{r READTARGETS}
read_targets <- read.delim("A_Targets_experiment.txt")
read_expression <- as.matrix(read.delim("expression.txt", header = TRUE, row.names = 1))
head(expression)

```

```{r}
myInfo=list(myName="Jaume Reig", myLab="Bioinformatics Lab",
myContact="jaume.reig@alum.esci.upf.edu", myTitle="Practical Exercise on ExpressionSets")
show(myInfo)
```


```{r}
show(read_targets)
dim(read_expression)
head(summary(read_expression))
```

```{r}
boxplot(read_expression)
```

```{r}
pat_data <- as.matrix(read.table("A_Targets_experiment.txt", row.names = 1, header = TRUE, sep = "\t"))
dim(pat_data)
summary(pat_data)
```

```{r}
metadata <- as.matrix(data.frame(labelDescription = c("Age", "Score"), row.names = c("age", "score")))

metadata
```


```{r}
require(Biobase)
columnDesc <- data.frame(labelDescription = c("ID", "TYPE_OF_EPOC", "TYPE_OF_PATIENT"))
myannotDF <- new("AnnotatedDataFrame", data = read_targets, varMetadata = columnDesc)
myannotDF
```

```{r}
Example_set <- ExpressionSet(assayData = read_expression, phen_data = metadata)
myEset <- ExpressionSet(read_expression)
myEset
```

```{r}
phenoData(myEset) <- myannotDF
phenoData(myEset)
```


```{r}
myDesc <- new("MIAME", name= myInfo[["myName"]],
lab= myInfo[["myLab"]],
contact= myInfo[["myContact"]] ,
title=myInfo[["myTitle"]])
print(myDesc)
```

